\documentclass[11pt]{report}
\usepackage[T1]{fontenc}
\usepackage[margin=1in, papersize={11in, 17in}]{geometry}
\usepackage{eurosym}
\usepackage{eurosym, fontspec, xltxtra, xunicode}
\pagenumbering{gobble}
\parindent=0pt
\parskip=24pt
\setmainfont{Adobe Garamond Pro}
\begin{document}

\textbf{POÈME RÉCURSIF} establishes a network of events that build up and tear
down pieces of rhythmic structure at one and the same time. The piece's
thousands of attack points structure hundreds of differently overlapping
rhythmic cells; moment-to-moment changes in the piece's surface result from
interplay of material in the horizontal and vertical directions at once.

\textbf{Realization.} The number of players is unspecified. Parts may be
assigned one to a player, more than one to a player or shared between players.
Instrumentation is unspecified beyond the designation of sixty-four untuned
parts as written into the score. A battery of African, Asian or Western
percussion instruments will give the piece a certain character; found
collections of wood, stone or metal will give the piece another character; the
repurposing of objects in the concert hall, street or studio will give the
piece a different character still. Choices of instrumentation, performance
space and the distribution of parts should all be made so as to reinforce the
shifting, dense character of the musical surface and the many attack points
that make it up. Attacks are all to be precise, well-articulated and of exactly
equal duration; the sustained parts of durations written into the score are
meaningless and there should be no difference between, for example, a quarter
note, on the one hand, and, on the other, a sixteenth note followed by three
sixteenth rests. The piece can be played either uniformly quietly or uniformly
loudly. In either case, changes in perceived dynamic are to be effected through
the entrance and exit of groups of players as indicated in the score. Contrast
dense sections of the piece with thinner sections and let the massiveness of
the rhythmic patterning vary accordingly. Tempo, once chosen, must remain
constant for any one performance but may vary from performance to performance
as indicated.

\textbf{Duration.} 6 to 7 minutes.

\vfill

\textbf{Po\`{e}me r\'{e}cursif} was written in 2003. The piece is dedicated to
Gy\"{o}rgy Ligeti and Beno\^{i}t Mandelbrot.

\end{document}
